Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
more ref cleanup

\section{CSIRO High Performance Compute Infrastructure}
CSIRO ASC shared facilities [10] are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to
derive data products (meshes). Raw data and meshes are ``bagged'' and stored in
the ASC archival system. ASC High Performance Compute (HPC) hosts (systems with
high processor count and large memory) are taken advantage of to create and
verify bags more rapidly than would be possible on conventional computer
systems.

@@

References
[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
[2] http://topbraid.org/spin/api/
[3] http://www.plantontology.org/
%[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
%[13] doi:10.1007/978-3-642-13654-2\_22
%[14] http://www.w3.org/DesignIssues/LinkedData.html

>>>>

\section{CSIRO High Performance Compute Infrastructure}
CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to
derive data products (meshes). Raw data and meshes are ``bagged'' and stored in
the ASC archival system. ASC High Performance Compute (HPC) hosts (systems with
high processor count and large memory) are taken advantage of to create and
verify bags more rapidly than would be possible on conventional computer
systems.

@@

References
[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
[2] http://topbraid.org/spin/api/
[3] http://www.plantontology.org/
%[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
%[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
%[13] doi:10.1007/978-3-642-13654-2\_22
%[14] http://www.w3.org/DesignIssues/LinkedData.html
